%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=blue!50!black
}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{0.9in}


\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Ayazhan Kadessova} \\ \vspace{1pt}
    \small Kowloon, Hong Kong $|$ \small (852) 9288-8547 $|$ \href{mailto:kadessovaayazhan@gmail.com}{\underline{kadessovaayazhan@gmail.com}} \\
    \vspace{1pt}
\href{https://linkedin.com/in/ayazhankad}{\underline{linkedin.com/in/ayazhankad}} $|$ \href{https://ayazhan-kadessova.netlify.app/}{\underline{Personal Website}} $|$ \href{https://github.com/ayazhankadessova}{\underline{github.com/ayazhankadessova}}
\end{center}
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {J.P.Morgan Chase \& Co.}{Jun. 2023 -- Aug. 2023}
      {Software Engineering Intern, Global Technology Infrastructure \& Tech Production Delivery}{Kowloon, Hong Kong}
          \resumeProjectHeading
          {\textbf{Streamlined Observability as Code and Automated CI/CD} $|$ \emph{Dynatrace, Terraform, Jenkins, Jules, Bash}}{}
          \resumeItemListStart
            \resumeItem{Implemented Terraform automation for synthetic monitoring, custom email alerting, maintenance window setup in Dynatrace for the services necessary to validate and execute various product portfolios within in-house application, enabling effective optimization and reducing setup time.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Overall Application Health Monitoring} $|$ \emph{Grafana, Gaia Portal}}{}
          \resumeItemListStart
            \resumeItem{Built a Health Dashboard in Grafana implementing event listeners for custom APIs to monitor over 30 services in a production environment, including monitoring expiring certificates and system performance of an in-house application.}
            \resumeItem{Achieved beter user experience via logical data groupings, categorized severity-based alerts, defined trigger conditions and notification groups.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Diversity, Equity, Inclusion Chatbot} $|$ \emph{Nodejs, Typescript, API}}{}
          \resumeItemListStart
            \resumeItem{Led a team of three backend developer interns within a larger team of six to build a full-stack chatbot that utilizes NLP model fine-tuned on internal documentation to provide guidance on fostering a diverse work environment at JP Morgan. }
          \resumeItemListEnd
\vspace{2pt}   
    \resumeSubheading
      {Super Cat Technology Limited}{June 2022 - Sep. 2022}
      {Natural Language Processing Engineer}{Kowloon, Hong Kong}
       \resumeProjectHeading
          {\underline{\href{https://example.com}{\textbf{Automated Machine Learning}}} $|$ \emph{Python, PyCaret, MongoDB, Fastapi, Streamlit}}{}
          \resumeItemListStart
            \resumeItem{Developed the Classification component of AutoML, utilizing user-defined criteria to identify optimal ML models for input data and accurately classify target data, resulting in improved customer churn prediction for client companies.}
            \resumeItem{Boosted T5-based Table QA accuracy from 60\% to 88\% by filtering columns through semantic search and checking their relevancy.}
          \resumeItemListEnd

       \resumeProjectHeading
       {\underline{\href{https://github.com/ayazhankadessova/Portfolio-Projects/tree/main/Fine_Tune_Sentiment_Analysis}{\textbf{Automated Multi-label text classification}}} $|$ \emph{Python, PyTorch, transformers}}{}  
          \resumeItemListStart
            \resumeItem{Upgraded text classification model from binary (positive/negative) to multi-label (1-5), integrating it into the Performance Analysis pipeline, enabling more comprehensive customer feedback insight and enhancing the customer service software's query prioritization capabilities.}
          \resumeItemListEnd
\vspace{2pt}  
    \resumeSubheading
      {Alphalex Capital Management}{Mar. 2022 -- May 2022}
      {IT Investment Intern}{Central, Hong Kong}
      \resumeItemListStart
        \resumeItem{Created \underline{\href{https://github.com/ayazhankadessova/Internship_Spring2022/tree/main/Cadence_NFT_(FLOW)}{\textbf{NFT Collection (ERC-721A)}}} using Cadence to compare the user-friendliness of wallets associated with FLOW, Ethereum blockchains.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hong Kong Baptist University}{Kowloon, Hong Kong}
      {BSc (Hons) in Computer Science, cGPA: 3.92/4.0, top 1\% of class}{Sep. 2021 -- Exp. 2025} \\
    \vspace{0.2cm}
  \resumeSubHeadingListEnd
   \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Relevant Computer Science Courses}{: Data Structures and Algorithms; Database Management; Python; Java; Statistics, Probability, Calculus; Applied Linear Algebra; Causal Inference with R; Cybersecurity and Data Privacy.} \\
     \textbf{Relevant Finance Courses}{: Investment Management; Unveil the Numbers Before You Invest; Financial Management; Basic Economic Principles.} \\
     \textbf{Awards}{: Finalist of IFTA Fintech and Innovation Awards 2023; \underline{\href{https://www.comp.hkbu.edu.hk/v1/?page=std_ach&id=182}{\textbf{3rd team place in AUHack}}} Hackathon by Aarhus University in Denmark; \underline{\href{https://www.comp.hkbu.edu.hk/v1/?page=std_ach&id=181}{\textbf{Finalist of Techathon 2023}}} by HKSTP; Finalist of Quest for Securities \& Investment Elites (QSIE) Case Analysis Competition 2022.} \\ \underline{\href{https://www.comp.hkbu.edu.hk/v1/?page=std_ach&id=182}{\textbf{CS Department Award 2022 \& 2023}}}{: Recognized twice for Research on Location System contribution and mentoring 6 freshmen among 404 students.} \\
    }}    
 \end{itemize}

 %-----------Activities-----------
\section{Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Goldman Sachs}{May 2023}
      {Women’s Trader Academy}{Central, Hong Kong}
      \resumeItemListStart
        \resumeItem{Ranked Top 3 in Equity trading simulation and gained practical expertise in FX and Equities trading, Market Making fundamentals.}
      \resumeItemListEnd
       \resumeSubheading
      {Google}{Sep. 2022 -- May 2023}
      {Women Techmakers Ambassador}{Central, Hong Kong}
      \resumeItemListStart
        \resumeItem{Awarded Google Generation Scholarship for organizing initiatives to promote inclusion, focusing on empowering women in tech.}
        \resumeItem{Conducted hands-on \underline{\href{https://www.linkedin.com/posts/ayazhankad_today-i-was-the-speaker-for-the-hands-on-activity-7038903549317050368-JdYM?utm_source=share&utm_medium=member_desktop}{\textbf{web scraping using Python workshop}}} for 100 participants with various tech and non-tech backgrounds. }
      \resumeItemListEnd
\resumeSubHeadingListEnd
      
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 - Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\underline{\href{https://ayazhankad-coding.blogspot.com/2021/09/scraping-fafakz-for-almaty-delivery.html}{\textbf{FAFA, cargo transportation business model}}} $|$ \emph{Python, Beautiful Soup, Web Scraping, Data Science}}{}
          \resumeItemListStart
            \resumeItem{Developed an open-source project involving web scraping of cargo transportation data from websites in Kazakhstan and the CIS.}
            \resumeItem{Conducted data analysis and authored a comprehensive post to suggest top three profitable business models, considering route, truck type, products.}
          \resumeItemListEnd

      \resumeProjectHeading
{\underline{\href{https://github.com/ayazhankadessova/FinanceGame}{\textbf{LEarnBU}}} $|$ \emph{HTML, CSS, Javascript, Financial Management}}{}
          \resumeItemListStart
            \resumeItem{Created a web-based financial literacy game with different storylines for each character to help 50 HKBU students learn personal financing. }
            \resumeItem{Based on pre-game and post-game scores, helped 82\% of students acquire knowledge in investing, retirement planning, deposit and credit plans.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Certificates}{: \underline{\href{https://www.credly.com/badges/52b619d0-9304-4a6f-bc22-3f05b057113c/linked_in_profile}{\textbf{Hashicorp Certified – Terraform Associate (003)}}}, \underline{\href{https://www.linkedin.com/posts/ayazhankad_aws-machine-learning-foundations-2022-activity-7001448530271772672-53pA?utm_source=share&utm_medium=member_desktop}{\textbf{AWS Machine Learning Foundations.}}}} \\
     \textbf{Languages}{: Python (proficient), Java/SQL/JavaScript/HTML/CSS (intermediate), TypeScript/C++ (prior experience).} \\
     \textbf{Frameworks and Tools}{: Terraform/Git (proficient), NodeJS/React.js (intermediate), Dynatrace, Jenkins, Jules, Cloud(AWS, Azure).}}}
 \end{itemize}
%-------------------------------------------
\end{document}
